---
title: "SQuID"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    theme: cosmo
    css: css/stylesheet.css
runtime: shiny_prerendered
description: >
  SQuID integrated learning environment
---
<!--bootstrap, cerulean, cosmo, darkly, flatly, journal, lumen, paper, readable, sandstone, simplex, spacelab, united, yeti rmarkdown themes-->
```{r setup, include=FALSE}
#devtools::install_github("rundel/learnrhash")
library(shiny)
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
source("./variables/var_general.R")
source("./variables/var_fullmodel.R")
source("./variables/var_modules.R")
source("./text/text.R")  
#any text with equation in it should be wrapped in a <p></p> in order for cat(.) to properly print it. 
#but not titles because then things get messed up.
for(i in 1:length(text)){
  list.idx <- !grepl("*[t]itle*|*image*",names(text[[i]]),ignore.case = T)
  if(any(list.idx)){
    text[[i]][list.idx] <- rapply(text[[i]][list.idx],function(x)paste0("<p>",x,"</p>"),how="replace")
  }
}
#place each list element into the global environment
list2env(text, names(text),envir=.GlobalEnv)
source("./submission.R")
 
# display R code in console format
displayRCode <- function(RCode){
  return(wellPanel(class="highlight-source-r ", HTML(paste0("<h3>R code:</h3>", RCode))))
}
tut_reptitle <- "SQuID course"

#code to allow a certain amount of retries: question_module_server_impl <- function(
question_module_server_impl <-function (input, output, session, question, question_state = NULL) 
{
  ns <- getDefaultReactiveDomain()$ns
  # new ============================
  # set counter
  val <- reactiveValues(
    numtry = 0
  )
  # ================================
  
  question$seed <- learnr:::random_seed()
  submitted_answer <- reactiveVal(NULL, label = "submitted_answer")
  is_correct_info <- reactive(label = "is_correct_info", {
    if (is.null(submitted_answer())) 
      return(NULL)
    ret <- question_is_correct(question, submitted_answer())
    # new : Increment counter =======
    isolate(val$numtry <- val$numtry+1)
    # ===============================
    if (!inherits(ret, "learnr_mark_as")) {
      stop("`question_is_correct(question, input$answer)` must return a result from `correct`, `incorrect`, or `mark_as`")
    }
    ret
  })
  is_done <- reactive(label = "is_done", {
    if (is.null(is_correct_info())) 
      return(NULL)
    # updated ====================================================
    (!isTRUE(question$allow_retry>0)) || is_correct_info()$correct
    # ============================================================
  })
  button_type <- reactive(label = "button type", {
    if (is.null(submitted_answer())) {
      "submit"
    }
    else {
      if (is.null(is_correct_info())) {
        stop("`is_correct_info()` is `NULL` in a place it shouldn't be")
      }
      if (is_correct_info()$correct) {
        "correct"
      } else {
        # not correct
        # updated =====================================
        if (isTRUE(val$numtry<question$allow_retry)|(question$allow_retry&is.logical(question$allow_retry))) {
          # not correct, but may try again
          "try_again"
        } else {
          # not correct and can not try again
          "incorrect"
        }
      }
    }
  })
  answer_is_valid <- reactive(label = "answer_is_valid", {
    if (is.null(submitted_answer())) {
      learnr:::question_is_valid(question, input$answer)
    }
    else {
      learnr:::question_is_valid(question, submitted_answer())
    }
  })
  init_question <- function(restoreValue = NULL) {
    if (question$random_answer_order) {
      is_visible_option <- !learnr:::answer_type_is_function(question$answers)
      question$answers[is_visible_option] <<- learnr:::shuffle(question$answers[is_visible_option])
    }
    submitted_answer(restoreValue)
  }
  past_submission_answer <- learnr:::retrieve_question_submission_answer(session, 
                                                                question$label)
  init_question(past_submission_answer)
  output$action_button_container <- renderUI({
    learnr:::question_button_label(question, button_type(), answer_is_valid())
  })
  output$message_container <- renderUI({
    req(!is.null(is_correct_info()), !is.null(is_done()))
    learnr:::withLearnrMathJax(learnr:::question_messages(question, messages = is_correct_info()$messages, 
                                        is_correct = is_correct_info()$correct, is_done = is_done()))
  })
  output$answer_container <- renderUI({
    if (is.null(submitted_answer())) {
      return(learnr:::withLearnrMathJax(question_ui_initialize(question, 
                                                      isolate(input$answer))))
    }
    if (is.null(is_done())) {
      return(NULL)
    }
    if (is_done()) {
      return(learnr:::withLearnrMathJax(question_ui_completed(question, 
                                                     submitted_answer())))
    }
    return(learnr:::withLearnrMathJax(question_ui_try_again(question, 
                                                   submitted_answer())))
  })
  observeEvent(input$action_button, {
    if (button_type() == "try_again") {
      submitted_answer(NULL)
      learnr:::event_trigger(session, "reset_question_submission", 
                    data = list(label = as.character(question$label), 
                                question = as.character(question$question)))
      return()
    }
    submitted_answer(input$answer)
    learnr:::event_trigger(session = session, event = "question_submission", 
                  data = list(label = as.character(question$label), 
                              question = as.character(question$question), answer = as.character(input$answer), 
                              correct = is_correct_info()$correct))
  })
  observe({
    req(submitted_answer(), is.reactive(question_state))
    current_answer_state <- list(type = "question", answer = submitted_answer(), 
                                 correct = is_correct_info()$correct)
    question_state(current_answer_state)
  })
}
assignInNamespace("question_module_server_impl",question_module_server_impl,ns="learnr")

```

## Start

```{r portal, results="asis"}
#1st section
      cat("###",portal_txt$parag0_title)

      cat(portal_txt$patag1_image)
      HTML(portal_txt$parag0_contents_1)
      cat(portal_txt$parag0_contents_2)

      #2nd section
      cat("###","Guidance for Users")
            
      fluidRow(
        column(width = 4,
          h5("For Beginners"),
          HTML(portal_txt$beginners)
        ),
        column(width = 4,
          h5("For Teachers"),
          HTML(portal_txt$teachers)
        ),
        column(width = 4,
          h5("For Experts"),
          HTML(portal_txt$experts)
        )
      )
      

      #3rd section
      cat("###",portal_txt$parag3_title)

      HTML(portal_txt$parag3_contents1)
      cat(portal_txt$parag3_contents2)

      cat(portal_txt$patag3_image)

      p(strong("References:"))
      p(HTML("Allegue, H., Araya-Ajoy, Y. G., Dingemanse, N. J., Dochtermann, N. A., Garamszegi, L. Z., 
              Nakagawa, S., Réale, D., Schielzeth, H.& Westneat, D. F. (2016) Statistical Quantification of 
              Individual Differences: an educational and statistical tool for understanding multi-level phenotypic 
              data in linear mixed models. <i>Methods in Ecology and Evolution</i>, 8, 257-267.
              <a href='https://doi.org/10.1111/2041-210X.12659' target='_blank'>doi: 10.1111/2041-210X.12659</a>"))
      p(HTML("Dingemanse, N. J.& Dochtermann, N. A. (2013) Quantifying individual variation in behaviour: 
              mixed-effect modelling approaches. <i>Journal of Animal Ecology</i>, 82, 39-54.
              <a href='https://doi.org/10.1111/1365-2656.12013' target='_blank'>doi: 10.1111/1365-2656.12013</a>"))



```

###  Shiny

We will make use of various shiny apps throughout this course to present key concepts in exploring individual differences and multilevel variation. A list ,and the code, for all shiny apps is available [here](https://github.com/squidgroup/squidEducApp).

```{r quiz1, echo = FALSE}
question("Which answer describes you best?",
  answer("Beginner: I have little knowledge of LMMs or multilevel variation.", message = "Start with Module 1", correct = TRUE),
  answer("Intermediate user: I have prior knowledge of LMMs, multilevel variation, and/or statistical distributions.", message = "*Start with Module 3", correct = TRUE),
  answer("Expert: I have extensive knowledge of the mixed-effects modeling framework and individual differences.", message = "Fully explore the SQuID concept with the 'full model' modules", correct = TRUE),
  answer("Teacher: I want my student to learn about mixed-effects models and patterns of phenotypic variance. ", message = "*Please skim the module titles to assess which are of most use for your student", correct = TRUE),
  answer("None of the above.", correct = FALSE),
  type = "single",
  incorrect = "Eek, this might not  be the right place for you.",
  correct=NULL
)

```

```{r quiz2}
question("Which is good",answer("good",correct=TRUE),
         answer("bad",correct=F),
         allow_retry=2)
```
### (optional) Save progress report

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```

<!-- <object data='https://bertvdveen.shinyapps.io/app1/' frameborder="0" style="width: 100%; height: 850px;overflow:hidden;display:block"></object> 

```{r quizn, echo = FALSE}
question("What did you explore in the above app?",
  answer("Measurement error", correct = TRUE),
  answer("Number of individuals", correct = FALSE),
  type = "learnr_radio",
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```
-->

## Module 1: Basic lessons about variance

```{r mod1_step1_title, results="asis"}
  cat("###",Mod1Step1_txt$title)
```

```{r mod1_step1, results="asis"}
  #### Subgoal ####
  cat(Mod1Step1_txt$subgoal)   # Text: subgoal
  #### Introduction ####
  cat(Mod1Step1_txt$intro)      # Text: introduction

  
cat(Mod1Step1_txt$para1) # Text: Paragraph 1
 
cat(Mod1Step1_txt$explanation1)  # Text: Notation explanation

    #### Exercice ####
    cat(Mod1Step1_txt$exercise)   # Text: exercise
    cat(placeholder_image)
    
  #### Point ####
    cat(Mod1Step1_txt$point) # Text: point
  #### Solution ####
  cat(Mod1Step1_txt$solutions)   # Text: solutions
  
  #### Statistical model ####
  cat(module1_txt$statModTitle)
  cat(Mod1Step1_txt$statmodel1)        # Text: statistical model paragraph 1
  #### Eqaution 1 ####
  p(paste("$$",NOT$trait.1,"_{",NOT$time,NOT$ind,"}=",NOT$devI,"_",NOT$ind,"+",NOT$error,"_{",NOT$time,NOT$ind,"}$$",sep=""))
  cat(Mod1Step1_txt$statmodel2) # Text: statistical model paragraph 2

  cat(Mod1Step1_txt$statmodel3)  # Text: statistical model paragraph 3
  #### Eqaution 2 ####
  p(paste("$$V_p=V_",NOT$devI,"+V_",NOT$mError,"$$",sep=""))
```

```{r mod1_step2_title, results="asis"}
  cat("###",Mod1Step2_txt$title)
```

```{r mod1_step2, results="asis"}
  cat(Mod1Step2_txt$subgoal)    # Text: subgoal
  cat(Mod1Step2_txt$intro)      # Text: introduction
  cat(Mod1Step2_txt$exercise)   # Text: exercise
  cat(placeholder_image)
  
  cat(Mod1Step2_txt$para1)  # Text: paragraph 1

  cat(Mod1Step2_txt$para2)
  
  cat(Mod1Step2_txt$para3)  # Text: paragraph 3
  
    cat(Mod1Step4_txt$para3)    # Text: statistical result
    cat(Mod1Step2_txt$point)  # Text: point
  
    cat(Mod1Step2_txt$para4)  # Text: paragraph 4
    p(withMathJax(paste("$$Repeatability=\\frac{V^\\prime_",NOT$devI,"}{V^\\prime_",NOT$devI,"+V^\\prime_",NOT$mError,"}$$",sep="")))
    
    cat(Mod1Step2_txt$para5)  # Text: paragraph 5
  
    # Scatter plot: measurements correlation
    cat(Mod1Step2_txt$para6)  # Text: paragraph 6
  
  cat(module1_txt$statModTitle)
  p(paste("$$",NOT$trait.1,"_{",NOT$time,NOT$ind,"}=",NOT$devI,"_",NOT$ind,"+",NOT$error,"_{",NOT$time,NOT$ind,"}$$",sep=""))
  p(paste("$$V_",NOT$total,"=V_",NOT$devI,"+V_",NOT$mError,"$$",sep=""))
```

```{r mod1_step3_title, results="asis"}
cat("###",Mod1Step3_txt$title)
```

```{r mod1_step3, results="asis"}
  cat(Mod1Step3_txt$subgoal)   # Text: subgoal
  cat(Mod1Step3_txt$intro)     # Text: introduction
  cat(Mod1Step3_txt$exercise)  # Text: exercise
  cat(Mod1Step3_txt$exercise2) # Text: exercise 2
  
  cat(placeholder_image) #app

    cat(Mod1Step4_txt$para3)    # Text: statistical result

  # Repeatability equation
  cat(Mod1Step3_txt$para1)         # Text: paragraph 1
  p(paste("$$Repeatability=\\frac{V^\\prime_",NOT$devI,"}{V^\\prime_",NOT$devI,"+V^\\prime_",NOT$residualUpper,"}$$",sep=""))

  cat(Mod1Step3_txt$point)        # Text: point
  cat(Mod1Step3_txt$point2)       # Text: point 2
  cat(Mod1Step3_txt$point3)       # Text: point 3

  cat(module1_txt$statModTitle)
  cat(Mod1Step3_txt$statmodel)       # Text: statistical model 1
  p(paste("$$",NOT$trait.1,"_{",NOT$time,NOT$ind,"}=",
          NOT$devI,"_",NOT$ind,"+",
          NOT$error,"_{",NOT$time,NOT$ind,"}$$",sep=""))
  cat(Mod1Step3_txt$statmodel2)     # Text: statistical model 2
  p("The variance equation is now")
  p(paste("$$V_",NOT$total,"=V_",NOT$devI,"+V_",NOT$residualUpper,"$$",sep=""))
  p("where")
  p(paste("$$V_",NOT$residualUpper,"=V_{",NOT$mean," ",NOT$env,"}+V_",NOT$mError,"$$",sep=""))
```

```{r ex1-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(squidSim)
library(lme4)

get_data <- function(n,r,Vi,Vr){
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("individual(",n,")"), repeat_obs=r),
  parameters = list(
    individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    )
  )
)
  data <- get_population_data(squid_data)
  colnames(data)[c(1,4)] <- c("Phenotype","Individual")
  return(data)

}
```

```{r ex1, exercise=TRUE, warning=F, message=F}
# n is the number of individuals
# r is the number of repetitions for each individual
# Vi is the variance for individuals
# Vr is residual variance 
data <- get_data(n = 50, r = 2, Vi = 0.5, Vr = 0.5)
LMM <- lmer(Phenotype ~ 0 + (1|Individual), data = data)
summary(LMM)
```

```{r mod1_step4_title, results="asis"}
  cat("###",Mod1Step4_txt$title)
```

```{r mod1_step4, results="asis"}
  HTML(Mod1Step4_txt$subgoal)     # Text: subgoal
  cat(Mod1Step4_txt$intro)       # Text: introduction
  cat(Mod1Step4_txt$exercise)    # Text: exercise
      cat(placeholder_image)
      
  cat(Mod1Step4_txt$para1)    # Text: paragraph 1
  p(paste("$$",NOT$trait.1,"_{",NOT$time,NOT$ind,"}=",
          EQ3$mean0, "+",
          NOT$devI,"_",NOT$ind,"+",
          NOT$mean," ",
          NOT$env,"_{",NOT$time,NOT$ind,"} +",
          NOT$error,"_{",NOT$time,NOT$ind,"}$$",sep=""))
  cat(Mod1Step4_txt$para2)      # Text: paragraph 2

    cat(Mod1Step4_txt$para3)    # Text: paragraph 3
  
    cat(Mod1Step4_txt$para4)   # Text: paragraph 4
  cat(Mod1Step4_txt$para5)   # Text: paragraph 5
  cat(Mod1Step4_txt$para6)   # Text: paragraph 6
  cat(Mod1Step4_txt$point)   # Text: point
  
  cat(module1_txt$statModTitle)
  p(paste("$$",NOT$trait.1,"_{",NOT$time,NOT$ind,"}=",
          EQ3$mean0, "+",
          NOT$devI,"_",NOT$ind,"+",
          NOT$mean," ",
          NOT$env,"_{",NOT$time,NOT$ind,"} +",
          NOT$error,"_{",NOT$time,NOT$ind,"}$$",sep=""))
  p(paste("$$V_",NOT$total,"=V_",NOT$devI,"+V_{",NOT$mean," ",NOT$env,"}+V_",NOT$mError,"$$",sep=""))
```

## Module 2: Non-Gaussian traits

```{r mod2_step1_title, results="asis"}
cat("###", Mod2Step1_txt$title)
```

```{r mod2_step1, results="asis"}
  #### Title ####
  
  
  #### Subgoal ####
  cat(Mod2Step1_txt$subgoal)
  
  #### Introduction ####
  cat(Mod2Step1_txt$intro)

  cat(Mod2Step1_txt$para1)
  
  
  cat(Mod2Step1_txt$para1_image)
  cat(Mod2Step1_txt$para1_image_caption)

    cat(placeholder_image)

  cat(Mod2Step1_txt$para2)
  
  cat(Mod2Step1_txt$para3)

    cat(placeholder_image)

    
  cat(Mod2Step1_txt$para4)

  cat(Mod2Step1_txt$para5)
  
  cat("###",Mod2Step1_txt$para6_title)
  
  HTML(Mod2Step1_txt$para6)
  
  
  cat(Mod2Step1_txt$exercise)
  
    cat(placeholder_image)

  
  cat(Mod2Step1_txt$para7)

  cat("###", Mod2Step1_txt$para8_title)  
  
  HTML(Mod2Step1_txt$para8)
  
  cat("###",Mod2Step1_txt$para9_title)
  
  HTML(placeholder_image)

  
  HTML(Mod2Step1_txt$para9)
```


```{r mod2_step2_title, results="asis"}
cat("###", Mod2Step2_txt$title)
```

```{r mod2_step2, results="asis"}
  #### Subgoal ####
  cat(Mod2Step2_txt$subgoal)
  
  #### Introduction ####
  cat(Mod2Step2_txt$intro)
  
  cat(Mod2Step2_txt$para1)
  
  cat(Mod2Step2_txt$para1_eq1)
  cat(Mod2Step2_txt$para1_eq2)
  cat(Mod2Step2_txt$para1_eq3)
  
  cat(Mod2Step2_txt$para2)
  
  cat(Mod2Step2_txt$para2_eq1)
  cat(Mod2Step2_txt$para2_eq1)
  cat(Mod2Step2_txt$para2_eq1)
 
  cat(Mod2Step2_txt$para3)
  
  cat(Mod2Step2_txt$para3_eq1)
  cat(Mod2Step2_txt$para3_eq2)
  cat(Mod2Step2_txt$para3_eq3)
  
  cat(Mod2Step2_txt$para4)
  
  cat(Mod2Step2_txt$para4_eq1)
  
  cat(Mod2Step2_txt$exercise)
  

  cat(Mod2Step2_txt$para5)
  
    cat(placeholder_image)

```

```{r mod2_step3_title, results="asis"}
cat("###", Mod2Step3_txt$title)
```

```{r mod2_step3, results="asis"}
#### Subgoal ####
  cat(Mod2Step3_txt$subgoal)

  #### Introduction 1 ####
  cat(Mod2Step3_txt$para1)
  
  
  cat(Mod2Step3_txt$para1_eq1)
  cat(Mod2Step3_txt$para1_eq2)
  cat(Mod2Step3_txt$para1_eq3)
  
  cat(Mod2Step3_txt$para2)
  
  cat(Mod2Step3_txt$exercise)
  
    cat(placeholder_image)

```

```{r ex2, exercise=TRUE, warning=F, message=F}
# number of values generated
n <- 10000
# Use the Gaussian distribution to generate n values
# with a mean of 0 and a standard-deviation of 1.
y_prime <- rnorm(n, 0, 1)
# Convert these values to probabilities
# using the inverse-logit function.
p <- plogis(y_prime)
# Use the Bernoulli distribution to generate n values
# with the probability vector p.
y <- rbinom(n, size = 1, prob = p)
# Note that we used the binomial function with one trial,
# which is equivalent to the Bernoulli distribution.
```

```{r mod2_step3_con, results="asis"}
  cat(Mod2Step3_txt$para3)

  #### Introduction 2 ####
  cat(Mod2Step3_txt$intro2)
  
  cat(Mod2Step3_txt$intro2_eq1)
  cat(Mod2Step3_txt$intro2_eq2)
  cat(Mod2Step3_txt$intro2_eq3)
  cat(Mod2Step3_txt$intro2_e43)

  cat(Mod2Step3_txt$para4)
  
  cat(Mod2Step3_txt$para5)
  
  cat(Mod2Step3_txt$para5_eq1)
  cat(Mod2Step3_txt$para5_eq2)
  cat(Mod2Step3_txt$para5_eq3)
  cat(Mod2Step3_txt$para5_eq4)

  cat(Mod2Step3_txt$exercise2)
  
    cat(placeholder_image)

```

```{r ex3-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)
get_data <- function(n,r,Vi,Vr){
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("individual(",n,")"), repeat_obs=r),
  parameters = list(
    individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    )
  ),
  family = "poisson", 
  link = "log"
)
  data <- get_population_data(squid_data)
  colnames(data)[c(1,4)] <- c("Phenotype","Individual")
  return(data)
}
```

```{r ex3, exercise=TRUE, exercise=TRUE, warning=FALSE, message=FALSE}
# n is the number of individuals
# r is the number of repetitions for each individual
# Vi is the variance for individuals
# Vr is residual variance 
data <- get_data(n = 50, r = 2, Vi = 0.5, Vr = 0.5)
GLMM <- glmer(Phenotype ~ 0 + (1|Individual), family = poisson(link=log), data = data)
summary(GLMM)
```

```{r mod2_step3_con2, results="asis"}
  cat(Mod2Step3_txt$conclusion)
  
  p(strong("References:"))
  p(HTML("Nakagawa, S. & Schielzeth, H (2010) Repeatability for Gaussian and non-Gaussian data: a practical guide for biologists. 
          <i>Biological Reviews</i>, 85, 935-956.
          <a href='https://doi.org/10.1111/j.1469-185X.2010.00141.x' target='_blank'>doi: 10.1111/j.1469-185X.2010.00141.x</a>"))
```

## Module 3: Non-stochastic environments

```{r mod3_step1_title, results="asis"}

cat("###", Mod3Step1_txt$title)

```

```{r mod3_step1, results="asis"}
  cat(Mod3Step1_txt$subgoal)    # Text: subgoal
  cat(Mod3Step1_txt$intro)      # Text: introduction
  cat(Mod3Step1_txt$exercise)   # Text: exercise

  cat(Mod3Step1_txt$para1)      # Text: paragraph 1

  cat(placeholder_image)

  cat(Mod3Step1_txt$para2)       # Text: paragraph 2      
  cat(Mod3Step1_txt$para3)       # Text: paragraph 3
  
  # Figure of 2 examples of sampling design when among-individual variance in sampling timing is 0.1 and 0.9
  cat(Mod3Step1_txt$para3_image)
  cat(Mod3Step1_txt$para3_image_caption)
  
  cat(Mod3Step1_txt$para4)       # Text: paragraph 4
  
  cat(Mod3Step1_txt$para5)       # Text: paragraph 5
  
   cat(placeholder_image)

  cat(Mod3Step1_txt$results)     # Text: results
  
  cat(Mod3Step1_txt$para6)       # Text: para6
  
  p(paste0("$$",NOT$trait.1,"_{",NOT$time,NOT$ind,"}=",NOT$devI,"_",NOT$ind,"+",NOT$error,"_{",NOT$time,NOT$ind,"}$$"))
  
```

```{r mod3_step1_con, results="asis"}
  cat(Mod3Step1_txt$para7)       # Text: para7
  
  cat(Mod3Step1_txt$para8)       # Text: para8
  
  cat(Mod3Step1_txt$conclusion)  # Text: conclusion
  
  cat(Mod3Step1_txt$para9)       # Text: para9
  cat(Mod3Step1_txt$para10)      # Text: para10
  cat(Mod3Step1_txt$para11)      # Text: para11
```

```{r mod3_step2_title, results="asis"}
cat("###", Mod3Step2_txt$title)
```

```{r mod3_step2, results="asis"}
  cat(Mod3Step2_txt$subgoal)    # Text: subgoal
  cat(Mod3Step2_txt$intro)      # Text: introduction
  cat(Mod3Step2_txt$exercise)   # Text: exercise
  
    cat(placeholder_image)

  cat(Mod3Step2_txt$para1)      # Text: paragraph 1
  
    cat(placeholder_image)

  cat(Mod3Step2_txt$para2)      # Text: paragraph 2
  
  cat(Mod3Step2_txt$para3)      # Text: paragraph 3
  
  cat(Mod3Step2_txt$results)    # Text: results
  
  cat(Mod3Step2_txt$para4)      # Text: paragraph 4
  
  p(paste0("$$",NOT$trait.1,"_{",NOT$time,NOT$ind,"}=",NOT$devI,"_",NOT$ind,"+",NOT$error,"_{",NOT$time,NOT$ind,"}$$"))
  
  cat(Mod3Step2_txt$para5)      # Text: paragraph 5
  
    cat(placeholder_image)

  cat(Mod3Step2_txt$conclusion_title) # Text: conclusion
  
  cat(Mod3Step2_txt$para6)      # Text: paragraph 6
  
  cat(Mod3Step2_txt$para7)      # Text: paragraph 7
  
  cat(Mod3Step2_txt$para8)      # Text: paragraph 8
```

```{r mod3_step3_title, results="asis"}
cat("###", Mod3Step3_txt$title)
```

```{r mod3_step3, results="asis"}
  cat(Mod3Step3_txt$subgoal)    # Text: subgoal
  cat(Mod3Step3_txt$intro)      # Text: introduction
  cat(Mod3Step3_txt$exercise1)  # Text: exercise 1
  
    cat(placeholder_image)

  cat(Mod3Step3_txt$para1)      # Text: paragraph 1
  
    cat(placeholder_image)

  cat(Mod3Step3_txt$para2)      # Text: paragraph 2
  
  cat(Mod3Step3_txt$para3)      # Text: paragraph 3

  cat(placeholder_image)
  
  cat(Mod3Step3_txt$results)         # Text: results
  
  p(paste0("$$",NOT$trait.1,"_{",NOT$time,NOT$ind,"}=",EQ3$mean0,"+",NOT$devI,"_",NOT$ind,"+",NOT$mean," ",NOT$env,"+",NOT$error,"_{",NOT$time,NOT$ind,"}$$"))
```


```{r ex4-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)
get_data <- function(n,r,Vi,Vr){
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("individual(",n,")"), repeat_obs=r),
  parameters = list(
    individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    )
  )
)
  data <- get_population_data(squid_data)
  colnames(data)[c(1,4)] <- c("Phenotype","Individual")
  return(data)
}
```

```{r ex4, exercise=TRUE, exercise=TRUE, warning=FALSE, message=FALSE}
# n is the number of individuals
# r is the number of repetitions for each individual
# Vi is the variance for individuals
# Vr is residual variance 
data <- get_data(n = 50, r = 2, Vi = 0.5, Vr = 0.5)
LMM <- lmer(Phenotype ~ 1 + (1|Individual), data = data)
summary(LMM)
```

```{r mod3_step3_con, results="asis"}
  cat(Mod3Step3_txt$para4)      # Text: paragraph 4
  
  p(paste0("$$",NOT$trait.1,"_{",NOT$time,NOT$ind,"}=",EQ3$mean0,"+",NOT$devI,"_",NOT$ind,"+",NOT$error,"_{",NOT$time,NOT$ind,"}$$"))

  cat(Mod3Step3_txt$para5)      # Text: paragraph 5
  
    cat(placeholder_image)

  cat(Mod3Step3_txt$para6)      # Text: paragraph 6
  cat(Mod3Step3_txt$reminder)   # Text: notation reminder
  
  cat(Mod3Step3_txt$exercise2)  # Text: exercise 2
  
    cat(placeholder_image)

  cat(Mod3Step3_txt$para8)      # Text: paragraph 8
  
  cat(Mod3Step3_txt$para9)      # Text: paragraph 9
  
    cat(placeholder_image)

  cat(Mod3Step3_txt$conclusion) # Text: conclusion
  cat(Mod3Step3_txt$conclusion2) # Text: conclusion 2
  
  cat(Mod3Step3_txt$finalcaveat) # Text: a final caveat
  
```

## Module 4: Multiple traits

```{r mod4_step1_title, results="asis"}
cat("###", Mod4Step1_txt$title)
```


```{r mod4_step1, results="asis"}
  # Sub-goal
  cat(Mod4Step1_txt$subgoal)

    # Introduction
  cat(Mod4Step1_txt$intro)
  
  cat(Mod4Step1_txt$para1)
  
  # Exercise
  cat(Mod4Step1_txt$exercise)
  
  cat(Mod4Step1_txt$exercise_eq2)
  
  cat(Mod4Step1_txt$para2)

  cat(Mod4Step1_txt$para2_eq1)
  
  cat(Mod4Step1_txt$para3)
  
  cat(Mod4Step1_txt$para3_eq1)
  
  cat(placeholder_image)
  
  cat(Mod4Step1_txt$para4)

  cat(Mod4Step1_txt$para5)
  
  cat(Mod4Step1_txt$conclusion)
```

```{r mod4_step2_title, results="asis"}
cat("###",Mod4Step2_txt$title)
```

```{r mod4_step2, results="asis"}
  # Sub-goal
  cat(Mod4Step2_txt$subgoal)
  
  # Introduction
	cat(Mod4Step2_txt$intro)

	### Model equations
	cat(Mod4Step2_txt$intro_eq1)
	
	cat(Mod4Step2_txt$para1)

  ####### eq 1
  cat(Mod4Step2_txt$para1_eq1)
  
  cat(Mod4Step2_txt$para2)
  
  ####### eq 2 
  cat(Mod4Step2_txt$para2_eq1)
  
  cat(Mod4Step2_txt$para3)
  
  cat(Mod4Step2_txt$para4)
  
  cat(Mod4Step2_txt$para5)
  
  ####### eq 1
  cat(Mod4Step2_txt$para5_eq1)
  
  cat(Mod4Step2_txt$para6)
  
  cat(Mod4Step2_txt$para6_eq1)
  
  cat(Mod4Step2_txt$para7)

  cat(Mod4Step2_txt$para8)
  cat(Mod4Step2_txt$para8_eq1)
 
  cat(placeholder_image)


  cat(Mod4Step2_txt$para9)
  cat(Mod4Step2_txt$para9_eq1)

  cat(Mod4Step2_txt$para10)
  ####### eq 1
  cat(Mod4Step2_txt$para10_eq1)

  cat(Mod4Step2_txt$para11)
  
  cat(Mod4Step2_txt$para11_eq1)
  
  cat(Mod4Step2_txt$para12)
  
  cat(Mod4Step2_txt$conclusion)
  
  p(strong("References:"))
  p(HTML("Dingemanse, N.J. & Dochtermann, N.A. (2013) Quantifying individual variation in behaviour: 
         mixed-effect modelling approaches. <i>Journal of Animal Ecology</i>, 82, 39-54.
         <a href='https://doi.org/10.1111/1365-2656.12013' target='_blank'>doi: 10.1111/1365-2656.12013</a>"))
  p(HTML('Dingemanse, N.J., Dochtermann, N.A. & Nakagawa, S. (2012) Defining behavioural syndromes and the role of 
         "syndrome deviation" to study its evolution. <i>Behavioral Ecology and Sociobiology</i>, 66, 1543-1548.
         <a href="https://doi.org/10.1007/s00265-012-1416-2" target="_blank">doi: 10.1007/s00265-012-1416-2</a>'))
  p(HTML("Nicolaus, M., Brommer, J.E., Ubels, R., Tinbergen, J.M. & Dingemanse, N.J. (2013) 
          Exploring patterns of variation in clutch size-density reaction norms in a wild passerine bird. 
          <i>Journal of Evolutionary Biology</i>, 26, 2031-2043.
          <a href='https://doi.org/10.1111/jeb.12210' target='_blank'>doi: 10.1111/jeb.12210</a>"))
	
```

```{r mod4_step3_title, results="asis"}
cat("###",Mod4Step3_txt$title)
```

```{r Mod4Step3, results="asis"}
	# Sub-goal
  cat(Mod4Step3_txt$subgoal)	
	
 cat(Mod4Step3_txt$intro)
	
	# Exercise
  cat(Mod4Step3_txt$exercise)	

  cat(placeholder_image)

  cat(placeholder_image)

	cat(Mod4Step3_txt$results)
	cat(Mod4Step3_txt$results_eq1)
	
	cat(Mod4Step3_txt$para1)
	cat(Mod4Step3_txt$para1_eq1)


	cat(Mod4Step3_txt$para2)
	
	cat(Mod4Step3_txt$para2_eq1)
	
	cat(Mod4Step3_txt$para3)
	
	cat(Mod4Step3_txt$para4)

	cat(Mod4Step3_txt$conclusion)

	p(strong("References:"))
	p(HTML("van Noordwijk, A.J. & de Jong, G. (1986) Acquisition and allocation of resources - 
	       Their influence on variation in life-history tactics. <i>American Naturalist</i>, 128, 137-142.
	       <a href='https://doi.org/10.1086/284547' target='_blank'>doi: 10.1086/284547</a>"))
```

```{r mod4_step4_title,results="asis"}
cat("###",Mod4Step4_txt$title)
```

```{r mod4_step4,results="asis"}
	# Sub-goal
	cat(Mod4Step4_txt$subgoal)
	
	
	cat(Mod4Step4_txt$intro)
	
	cat(Mod4Step4_txt$intro_eq1)
	
	cat(Mod4Step4_txt$para1)
	
	cat(Mod4Step4_txt$para1_eq1)
	
	cat(Mod4Step4_txt$para2)
	
	cat(Mod4Step4_txt$para2_eq1)
	
	cat(Mod4Step4_txt$para3)

	cat(Mod4Step4_txt$para3_eq1)
	
  cat(Mod4Step4_txt$para4)
	
	
	cat(Mod4Step4_txt$para4_eq1)
	
	cat(Mod4Step4_txt$para5)
	
	cat(Mod4Step4_txt$para5_eq1)
	
	cat(Mod4Step4_txt$para6)
	
	cat(Mod4Step4_txt$para6_eq1)
	
	cat(Mod4Step4_txt$para7)
	
	cat(Mod4Step4_txt$para7_eq1)
	
	cat(Mod4Step4_txt$para8)
	
	cat(Mod4Step4_txt$para8_eq1)
	
	cat(Mod4Step4_txt$conclusion)
```

```{r mod4_step5_title, results = "asis"}
	cat("###",Mod4Step5_txt$title)
```

```{r mod4_step5, results = "asis"}
	# Sub-goal
	cat(Mod4Step5_txt$subgoal)

	# Introduction
	cat(Mod4Step5_txt$intro)

	cat(Mod4Step5_txt$intro_eq1)
	
  cat(Mod4Step5_txt$para1)
	
	cat(Mod4Step5_txt$para1_eq1)

	cat(Mod4Step5_txt$para2)
	
	# Exercise
	cat(Mod4Step5_txt$exercise)
    
	cat(placeholder_image)
	
	cat(Mod4Step5_txt$para3)
	
	cat(Mod4Step5_txt$para3_eq1)
	
	cat(Mod4Step5_txt$para4)

	cat(Mod4Step5_txt$para4_eq1)

  cat(placeholder_image)
```

```{r ex5-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(brms)
library(squidSim)

get_data <- function(n,r,Vi,Vr){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("individual(",n,")"), repeat_obs=r),
  n_response = 2,
  parameters=list(
    individual = list(
      vcov = matrix(c(1,Vi,Vi,1),nrow=2,ncol=2)
    ),
    residual = list(
      vcov = matrix(c(1,Vr,Vr,1),nrow = 2,ncol = 2)
    )
  )  
)
  data <- get_population_data(squid_data)
  colnames(data)[c(1,2,7)] <- c("Phenotype_1","Phenotype_2","Individual")
  return(data)

}
```

```{r ex5, exercise=TRUE, exercise.timelimit	= 300}
data <- get_data(n = 50, r = 2,  Vi = 0.5, Vr = 0.5)
bLMM <- brm(mvbind(Phenotype_1, Phenotype_2) ~ (1|Individual), data = data, silent = 0)
summary(bLMM)
```

```{r mod4_step5_con,results="asis"}
	cat(Mod4Step4_txt$para5)
	
	cat(Mod4Step5_txt$para5_eq1)

	cat(Mod4Step5_txt$para6)
	
	cat(Mod4Step5_txt$conclusion)
```