---
title: "SQuID"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    theme: cosmo
    css: css/stylesheet.css
runtime: shiny_prerendered
description: >
  SQuID integrated learning environment
---
<!--bootstrap, cerulean, cosmo, darkly, flatly, journal, lumen, paper, readable, sandstone, simplex, spacelab, united, yeti rmarkdown themes-->
```{r setup, include=FALSE}
#devtools::install_github("rundel/learnrhash")
library(shiny)
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
source("./variables/var_general.R")
source("./variables/var_fullmodel.R")
source("./variables/var_modules.R")
source("./text/text.R")  
#any text with equation in it should be wrapped in a <p></p> in order for cat(.) to properly print it. 
#but not titles because then things get messed up.
for(i in 1:length(text)){
  list.idx <- !grepl("*[t]itle*|*image*",names(text[[i]]),ignore.case = T)
  if(any(list.idx)){
    text[[i]][list.idx] <- rapply(text[[i]][list.idx],function(x)paste0("<p>",x,"</p>"),how="replace")
  }
}
#place each list element into the global environment
list2env(text, names(text),envir=.GlobalEnv)
source("./submission.R")
 
# display R code in console format
displayRCode <- function(RCode){
  return(wellPanel(class="highlight-source-r ", HTML(paste0("<h3>R code:</h3>", RCode))))
}
tut_reptitle <- "SQuID course"

#code to allow a certain amount of retries: question_module_server_impl <- function(
question_module_server_impl <-function (input, output, session, question, question_state = NULL) 
{
  ns <- getDefaultReactiveDomain()$ns
  # new ============================
  # set counter
  val <- reactiveValues(
    numtry = 0
  )
  # ================================
  
  question$seed <- learnr:::random_seed()
  submitted_answer <- reactiveVal(NULL, label = "submitted_answer")
  is_correct_info <- reactive(label = "is_correct_info", {
    if (is.null(submitted_answer())) 
      return(NULL)
    ret <- question_is_correct(question, submitted_answer())
    # new : Increment counter =======
    isolate(val$numtry <- val$numtry+1)
    # ===============================
    if (!inherits(ret, "learnr_mark_as")) {
      stop("`question_is_correct(question, input$answer)` must return a result from `correct`, `incorrect`, or `mark_as`")
    }
    ret
  })
  is_done <- reactive(label = "is_done", {
    if (is.null(is_correct_info())) 
      return(NULL)
    # updated ====================================================
    (!isTRUE(question$allow_retry>0)) || is_correct_info()$correct
    # ============================================================
  })
  button_type <- reactive(label = "button type", {
    if (is.null(submitted_answer())) {
      "submit"
    }
    else {
      if (is.null(is_correct_info())) {
        stop("`is_correct_info()` is `NULL` in a place it shouldn't be")
      }
      if (is_correct_info()$correct) {
        "correct"
      } else {
        # not correct
        # updated =====================================
        if (isTRUE(val$numtry<question$allow_retry)|(question$allow_retry&is.logical(question$allow_retry))) {
          # not correct, but may try again
          "try_again"
        } else {
          # not correct and can not try again
          "incorrect"
        }
      }
    }
  })
  answer_is_valid <- reactive(label = "answer_is_valid", {
    if (is.null(submitted_answer())) {
      learnr:::question_is_valid(question, input$answer)
    }
    else {
      learnr:::question_is_valid(question, submitted_answer())
    }
  })
  init_question <- function(restoreValue = NULL) {
    if (question$random_answer_order) {
      is_visible_option <- !learnr:::answer_type_is_function(question$answers)
      question$answers[is_visible_option] <<- learnr:::shuffle(question$answers[is_visible_option])
    }
    submitted_answer(restoreValue)
  }
  past_submission_answer <- learnr:::retrieve_question_submission_answer(session, 
                                                                question$label)
  init_question(past_submission_answer)
  output$action_button_container <- renderUI({
    learnr:::question_button_label(question, button_type(), answer_is_valid())
  })
  output$message_container <- renderUI({
    req(!is.null(is_correct_info()), !is.null(is_done()))
    learnr:::withLearnrMathJax(learnr:::question_messages(question, messages = is_correct_info()$messages, 
                                        is_correct = is_correct_info()$correct, is_done = is_done()))
  })
  output$answer_container <- renderUI({
    if (is.null(submitted_answer())) {
      return(learnr:::withLearnrMathJax(question_ui_initialize(question, 
                                                      isolate(input$answer))))
    }
    if (is.null(is_done())) {
      return(NULL)
    }
    if (is_done()) {
      return(learnr:::withLearnrMathJax(question_ui_completed(question, 
                                                     submitted_answer())))
    }
    return(learnr:::withLearnrMathJax(question_ui_try_again(question, 
                                                   submitted_answer())))
  })
  observeEvent(input$action_button, {
    if (button_type() == "try_again") {
      submitted_answer(NULL)
      learnr:::event_trigger(session, "reset_question_submission", 
                    data = list(label = as.character(question$label), 
                                question = as.character(question$question)))
      return()
    }
    submitted_answer(input$answer)
    learnr:::event_trigger(session = session, event = "question_submission", 
                  data = list(label = as.character(question$label), 
                              question = as.character(question$question), answer = as.character(input$answer), 
                              correct = is_correct_info()$correct))
  })
  observe({
    req(submitted_answer(), is.reactive(question_state))
    current_answer_state <- list(type = "question", answer = submitted_answer(), 
                                 correct = is_correct_info()$correct)
    question_state(current_answer_state)
  })
}
assignInNamespace("question_module_server_impl",question_module_server_impl,ns="learnr")

```

## Start

```{r portal, results="asis"}
#1st section
      cat("###",portal_txt$parag0_title)

      cat(portal_txt$parag1_image)
      HTML(portal_txt$parag0_contents_1)
      cat(portal_txt$parag0_contents_2)

      #2nd section
      cat("###","Guidance for Users")
            
      fluidRow(
        column(width = 4,
          h5("For Beginners"),
          HTML(portal_txt$beginners)
        ),
        column(width = 4,
          h5("For Teachers"),
          HTML(portal_txt$teachers)
        ),
        column(width = 4,
          h5("For Experts"),
          HTML(portal_txt$experts)
        )
      )
      

      #3rd section
      cat("###",portal_txt$parag3_title)

      HTML(portal_txt$parag3_contents1)
      cat(portal_txt$parag3_contents2)

      cat(portal_txt$patag3_image)

      p(strong("References"))
      p(HTML("Allegue, H., Araya-Ajoy, Y. G., Dingemanse, N. J., Dochtermann, N. A., Garamszegi, L. Z., 
              Nakagawa, S., Réale, D., Schielzeth, H.& Westneat, D. F. (2016) Statistical Quantification of 
              Individual Differences: an educational and statistical tool for understanding multi-level phenotypic 
              data in linear mixed models. <i>Methods in Ecology and Evolution</i>, 8, 257-267.
              <a href='https://doi.org/10.1111/2041-210X.12659' target='_blank'>doi: 10.1111/2041-210X.12659</a>"))
      p(HTML("Dingemanse, N. J.& Dochtermann, N. A. (2013) Quantifying individual variation in behaviour: 
              mixed-effect modelling approaches. <i>Journal of Animal Ecology</i>, 82, 39-54.
              <a href='https://doi.org/10.1111/1365-2656.12013' target='_blank'>doi: 10.1111/1365-2656.12013</a>"))



```

###  Shiny

We will make use of various shiny apps throughout this course to present key concepts in exploring individual differences and multilevel variation. A list,  and the code, for all shiny apps is available [on github](https://github.com/squidgroup/squidEducApp).

```{r quiz1, echo = FALSE}
question("Which answer describes you best?",
  answer("Beginner: I have little knowledge of LMMs or multilevel variation.", message = "Start with Module 1", correct = TRUE),
  answer("Intermediate user: I have prior knowledge of LMMs, multilevel variation, and/or statistical distributions.", message = "*Start with Module 2", correct = TRUE),
  answer("Expert: I have extensive knowledge of the mixed-effects modeling framework and individual differences.", message = "Fully explore the SQuID concept with the 'full model' modules", correct = TRUE),
  answer("Teacher: I want my student to learn about mixed-effects models and patterns of phenotypic variance. ", message = "*Please skim the module titles to assess which are of most use for your student", correct = TRUE),
  answer("None of the above.", correct = FALSE),
  type = "single",
  incorrect = "Eek, this might not  be the right place for you.",
  correct=NULL
)

```

<!--
```{r quiz2}
question("Which is good",answer("good",correct=TRUE),
         answer("bad",correct=F),
         allow_retry=2)
```
-->

<!-- <object data='https://bertvdveen.shinyapps.io/app1/' frameborder="0" style="width: 100%; height: 850px;overflow:hidden;display:block"></object> 

```{r quizn, echo = FALSE}
question("What did you explore in the above app?",
  answer("Measurement error", correct = TRUE),
  answer("Number of individuals", correct = FALSE),
  type = "learnr_radio",
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```
-->

## Module 1: Basic lessons about variance

```{r mod1_step1_title, results="asis"}
  cat("###",Mod1Step1_txt$title)
```

```{r mod1_step1, results="asis"}
  #### goal ####
  cat(Mod1Step1_txt$goal)   # Text: goal
  #### Introduction ####
  cat(Mod1Step1_txt$intro)      # Text: introduction

  
cat(Mod1Step1_txt$para1) # Text: Paragraph 1
 
cat(Mod1Step1_txt$explanation1)  # Text: Notation explanation

    #### Exercice ####
    cat(Mod1Step1_txt$exercise)   # Text: exercise
    
```

```{r app1, echo=FALSE, results="asis"}
cat(placeholder_image) #app1
```
 
 
```{r quiz1_app1, echo = FALSE}
question("Which answer describes you best?",
  answer("Beginner: I have little knowledge of LMMs or multilevel variation.", message = "Start with Module 1", correct = TRUE),
  answer("Intermediate user: I have prior knowledge of LMMs, multilevel variation, and/or statistical distributions.", message = "*Start with Module 2", correct = TRUE),
  answer("Expert: I have extensive knowledge of the mixed-effects modeling framework and individual differences.", message = "Fully explore the SQuID concept with the 'full model' modules", correct = TRUE),
  answer("Teacher: I want my student to learn about mixed-effects models and patterns of phenotypic variance. ", message = "*Please skim the module titles to assess which are of most use for your student", correct = TRUE),
  answer("None of the above.", correct = FALSE),
  type = "single",
  incorrect = "Eek, this might not  be the right place for you.",
  correct=NULL
)

```

```{r mod1_step1_con, results="asis"}
  #### Point ####
    cat(Mod1Step1_txt$point) # Text: point
  #### Solution ####
  cat(Mod1Step1_txt$solutions)   # Text: solutions
  
  #### Statistical model ####
  cat(Mod1Step1_txt$statModTitle)
  cat(Mod1Step1_txt$statmodel1)        # Text: statistical model paragraph 1
  #### Equation 1 ####
  cat(Mod1Step1_txt$statmodel1_eq1)
  
  cat(Mod1Step1_txt$statmodel2) # Text: statistical model paragraph 2

  cat(Mod1Step1_txt$statmodel3)  # Text: statistical model paragraph 3
  #### Equation 2 ####
  cat(Mod1Step1_txt$statmodel3_eq1)
```

```{r mod1_step2_title, results="asis"}
  cat("###",Mod1Step2_txt$title)
```

```{r mod1_step2, results="asis"}
  cat(Mod1Step2_txt$goal)    # Text: goal
  cat(Mod1Step2_txt$intro)      # Text: introduction
  cat(Mod1Step2_txt$exercise)   # Text: exercise
  
    cat(Mod1Step2_txt$para1)  # Text: paragraph 1
    
    cat(Mod1Step2_txt$para2)
```

```{r app2, echo=FALSE, results="asis"}
  cat(placeholder_image) #app2
```

```{r mod1_step2_con, results="asis"}
  cat(Mod1Step2_txt$para3)  # Text: paragraph 3
  
    cat(Mod1Step2_txt$point)  # Text: point
  
    cat(Mod1Step2_txt$para4)  # Text: paragraph 4
    cat(Mod1Step2_txt$para4_eq1)
    
    cat(Mod1Step2_txt$para5)  # Text: paragraph 5
  
    # Scatter plot: measurements correlation
    cat(Mod1Step2_txt$para6)  # Text: paragraph 6
```

```{r mod1_step3_title, results="asis"}
cat("###",Mod1Step3_txt$title)
```

```{r mod1_step3, results="asis"}
  cat(Mod1Step3_txt$goal)   # Text: goal
  cat(Mod1Step3_txt$intro)     # Text: introduction
  cat(Mod1Step3_txt$exercise)  # Text: exercise
  cat(Mod1Step3_txt$exercise2) # Text: exercise 2
```
```{r mod1_step3_app3, results="asis"}
  cat(placeholder_image) #app 3
```

```{r mod1_step3_con, results="asis"}

  # Repeatability equation
  cat(Mod1Step3_txt$para1)         # Text: paragraph 1
  cat(Mod1Step3_txt$para1_eq1)

  cat(Mod1Step3_txt$point)        # Text: point
  cat(Mod1Step3_txt$point2)       # Text: point 2

  cat(Mod1Step3_txt$statmodel)       # Text: statistical model 1
  cat(Mod1Step3_txt$statmodel_eq1)
  cat(Mod1Step3_txt$statmodel2)     # Text: statistical model 2
  cat(Mod1Step3_txt$statmodel2_eq1)
  p("where")
  cat(Mod1Step3_txt$statmodel2_eq2)
```

```{r ex1-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(squidSim)
library(lme4)

get_data <- function(n,r,Vi,Vr){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
  parameters = list(
    Individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    )
  ),
    response_names = "Phenotype"
)
  data <- get_population_data(squid_data)
  return(data)

}
```

```{r ex1, exercise=TRUE, warning=F, message=F}
# n is the number of individuals
# r is the number of repetitions for each individual
# Vi is the variance for individuals
# Vr is residual variance 
data <- get_data(n = 50, r = 2, Vi = 0.5, Vr = 0.5)
LMM <- lmer(Phenotype ~ 0 + (1|Individual), data = data)
summary(LMM)
```

```{r mod1_step4_title, results="asis"}
  cat("###",Mod1Step4_txt$title)
```

```{r mod1_step4, results="asis"}
  HTML(Mod1Step4_txt$goal)     # Text: goal
  cat(Mod1Step4_txt$intro)       # Text: introduction
  
  cat(Mod1Step4_txt$para1)    # Text: paragraph 1
  cat(Mod1Step4_txt$para1_eq1)
  cat(Mod1Step4_txt$para2)      # Text: paragraph 2

  cat(Mod1Step4_txt$exercise)    # Text: exercise
    cat(Mod1Step4_txt$para5)   # Text: paragraph 5

```
  
```{r mod1_step4_app4, results="asis"}
cat(placeholder_image)
```
  
```{r mod1_step4_con, results="asis"}      
  cat(Mod1Step4_txt$para4)   # Text: paragraph 4
  cat(Mod1Step4_txt$point)   # Text: point
  
  cat(Mod1Step1_txt$statModTitle)
  cat(Mod1Step4_txt$statMod_eq1)
  cat(Mod1Step4_txt$statMod_eq2)
```

## Module 2: Non-stochastic environments

```{r mod2_step1_title, results="asis"}

cat("###", Mod2Step1_txt$title)

```

```{r mod2_step1, results="asis"}
  cat(Mod2Step1_txt$goal)    # Text: goal
  cat(Mod2Step1_txt$intro)      # Text: introduction
  cat(Mod2Step1_txt$exercise)   # Text: exercise

  cat(Mod2Step1_txt$para1)      # Text: paragraph 1

  cat(Mod2Step1_txt$para2)       # Text: paragraph 2      
  
  cat(placeholder_image) #app 12
    
  cat(Mod2Step1_txt$para3)       # Text: paragraph 3
  
# Figure of 2 examples of sampling design when among-individual variance in sampling timing is 0.1 and 0.9
  cat(Mod2Step1_txt$para3_image)
  cat(Mod2Step1_txt$para3_image_caption)
  
  cat(Mod2Step1_txt$para4)       # Text: paragraph 4

  cat(placeholder_image) #app 13/14

  
  cat(Mod2Step1_txt$para5)       # Text: para6
  
  cat(Mod2Step1_txt$para5_eq1)       
```

```{r mod2_step1_con, results="asis"}
  cat(Mod2Step1_txt$para6)       # Text: para8
  
  cat(Mod2Step1_txt$conclusion)  # Text: conclusion
  
  cat(Mod2Step1_txt$para7)       # Text: para9
```

```{r mod2_step2_title, results="asis"}
cat("###", Mod2Step2_txt$title)
```

```{r mod2_step2, results="asis"}
  cat(Mod2Step2_txt$goal)    # Text: goal
  cat(Mod2Step2_txt$intro)      # Text: introduction
  cat(Mod2Step2_txt$exercise)   # Text: exercise
  
  cat(Mod2Step2_txt$para1)      # Text: paragraph 1
  
  cat(Mod2Step2_txt$para2)      # Text: paragraph 2

   cat(Mod2Step2_txt$para4)      # Text: paragraph 4
   cat(Mod2Step2_txt$para4_eq1)
   cat(Mod2Step2_txt$para5)      # Text: paragraph 5

  cat(placeholder_image) #app 15

  cat(Mod2Step2_txt$conclusion_title) # Text: conclusion
  
  cat(Mod2Step2_txt$para6)      # Text: paragraph 6
  
  cat(Mod2Step2_txt$para7)      # Text: paragraph 7
  
  cat(Mod2Step2_txt$para8)      # Text: paragraph 8
```

```{r mod2_step3_title, results="asis"}
cat("###", Mod2Step3_txt$title)
```

```{r mod2_step3, results="asis"}
  cat(Mod2Step3_txt$goal)    # Text: goal
  cat(Mod2Step3_txt$intro)      # Text: introduction
  cat(Mod2Step3_txt$exercise1)  # Text: exercise 1
  
  cat(Mod2Step3_txt$para1)      # Text: paragraph 1
  
  cat(Mod2Step3_txt$para2)      # Text: paragraph 2
  
  cat(Mod2Step3_txt$para3)      # Text: paragraph 3

  cat(Mod2Step3_txt$results)         # Text: results
  
  cat(Mod2Step3_txt$results_eq1)
```

```{r ex4-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)
get_data <- function(n,r,Vi,Vr){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
  parameters = list(
    Individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    )
  ),
  response_names = "Phenotype"

)
  data <- get_population_data(squid_data)
  return(data)
}
```

```{r ex4, exercise=TRUE, exercise=TRUE, warning=FALSE, message=FALSE}
# n is the number of individuals
# r is the number of repetitions for each individual
# Vi is the variance for individuals
# Vr is residual variance 
data <- get_data(n = 50, r = 2, Vi = 0.5, Vr = 0.5)
LMM <- lmer(Phenotype ~ 1 + (1|Individual), data = data)
summary(LMM)
```

```{r mod2_step3_con, results="asis"}
  cat(Mod2Step3_txt$para4)      # Text: paragraph 4
  
  cat(Mod2Step3_txt$para4_eq1)

  cat(Mod2Step3_txt$para5)      # Text: paragraph 6
  
    cat(placeholder_image) #app 16

  cat(Mod2Step3_txt$reminder)   # Text: notation reminder
  
  cat(Mod2Step3_txt$conclusion) # Text: conclusion
  cat(Mod2Step3_txt$conclusion2) # Text: conclusion 2
  
  cat(Mod2Step3_txt$finalcaveat) # Text: a final caveat
  
```


## Module 3: Random-slope regression

```{r mod3_step1_title, results="asis"}
  cat("###",Mod3Step1_txt$title)
```
```{r mod3_step1, results="asis"}
    cat(Mod3Step1_txt$goal)
    cat(Mod3Step1_txt$intro)
    cat(Mod3Step1_txt$exercise)
    
    cat(Mod3Step1_txt$exercise_eq1)

    displayRCode(Mod3Step1_txt$RCode1)
    
    cat(Mod3Step1_txt$para1)
    
    cat(Mod3Step1_txt$para1_eq1)
```    

```{r ex9-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)

get_data <- function(n,r,Vi,Vr, beta){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
  parameters=list(
    Individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    ),
     observation = list(
      names = "X1",
      beta = beta
    )
  ),
    response_names = "Phenotype"
)
  data <- get_population_data(squid_data)
  return(data)

}
```

```{r ex9, exercise=TRUE}
data <- get_data(n = 50, r = 2,  
                 Vi = 0.5, Vr = 0.5, 
                 beta = -0.4)
LMM <- lmer(Phenotype ~ 1 + X1 + (1|Individual), data = data)
summary(LMM)
```

```{r mod3_step1_con, results="asis"}
    cat(Mod3Step1_txt$para2)
    
    cat(placeholder_image)
    
    cat(Mod3Step1_txt$para3)
    
    cat(Mod3Step1_txt$results)
    
    cat(Mod3Step1_txt$para4)
    
    cat(Mod3Step1_txt$point)
    
    cat(Mod3Step1_txt$point_eq1)
    cat(Mod3Step1_txt$point_eq2)
    
    cat(Mod3Step1_txt$para5)
```

```{r ex10-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)

get_data <- function(n,r,Vi,Vr,Vs, Cis, beta){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
  parameters=list(
    Individual = list(
      names = c("ind_int","ind_slope"),
      beta  = c(1,0), #0 for no interaction
      vcov = c(Vi, Vs)
    ),
     observation = list(
      names = "X1",
      beta = beta[1]
    ),
     residual = list(
     vcov = Vr
    ),
        interactions = list(
      names = c("ind_slope:X1"),
      beta = c(1)
    )
  ),
  response_names = "Phenotype"
)
  data <- get_population_data(squid_data)
  return(data)

}
```

```{r ex10, exercise=TRUE}
data <- get_data(n = 100, r = 10,  
                 Vi = 1, Vr = 0.5, Vs = 0.5, 
                 beta = -0.4)
LMM <- lmer(Phenotype ~ 1 + X1 + (1 + X1||Individual), data = data)
summary(LMM)
```


```{r mod3_step2_title, results="asis"}

cat("###",Mod3Step2_txt$title)
```
```{r mod3_step2, results="asis"}
    cat(Mod3Step2_txt$goal)
    cat(Mod3Step2_txt$intro)
    cat(Mod3Step2_txt$para1)
    
    cat(Mod3Step2_txt$para1_eq1)
    
    cat(Mod3Step2_txt$para2)
    
    cat(Mod3Step2_txt$para2_eq1)
    
    cat(Mod3Step2_txt$para3)
    
    cat(Mod3Step2_txt$exercise)
    
    cat(Mod3Step2_txt$exercise_eq1)
    
    cat(Mod3Step2_txt$para4)
    
    cat(placeholder_image)
    
    cat(Mod3Step2_txt$results)
    
    cat(Mod3Step2_txt$para5)
    
    cat(Mod3Step2_txt$para6)
    cat(Mod3Step2_txt$point)
    
   cat(Mod3Step2_txt$point_eq1)
    p("where")
    cat(Mod3Step2_txt$point_eq2)
    
    cat(Mod3Step2_txt$para7)
```

```{r ex11-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)

get_data <- function(n,r,Vi,Vr,Vs, Cis, beta){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
   parameters = list(
    Individual = list(
      names = c("ind_int","ind_slope"), 
      beta = c(1,0),
      vcov = matrix(c(Vi,Cis,Cis,Vs),ncol=2,nrow=2)
    ),
    observation= list(
      names = "X1",
      beta = beta[1]
    ), 
    residual = list(
      vcov = Vr
    ),
    interactions = list(
      names = c("ind_slope:X1"),
      beta = 1
  )
  ),
  response_names = "Phenotype"
)
  data <- get_population_data(squid_data)
  return(data)

}
```

```{r ex11, exercise=TRUE}
data <- get_data(n = 300, r = 100,  
                 Vi = 1, Vr = 0.5, Vs = 1, 
                 Cis = 0.3, 
                 beta = -0.4)
LMM <- lmer(Phenotype ~ 1 + X1  + (1+X1|Individual), data = data)
summary(LMM)
```

```{r mod3_step3_title, results="asis"}
    cat("###",Mod3Step3_txt$title)
```
```{r mod3_step3, results="asis"}
    cat(Mod3Step3_txt$goal)
    cat(Mod3Step3_txt$intro)
    cat(Mod3Step3_txt$exercise)
    
    cat(Mod3Step3_txt$exercise_eq1)
    
    cat(placeholder_image)
    
    cat(Mod3Step3_txt$para1)
    cat(Mod3Step3_txt$para2)
  
    cat(Mod3Step3_txt$para3)
    
    cat(placeholder_image)
           
    cat(Mod3Step3_txt$para4)
```


## Module 4: Multi-dimensional Phenotypic Plasticity (MDPP)

```{r mod4_step1_title, results="asis"}
cat("###", Mod4Step1_txt$title)
```


```{r mod4_step1, results="asis"}
  # Sub-goal
  cat(Mod4Step1_txt$goal)

  # Introduction
  cat(Mod4Step1_txt$intro)

  # Exercise
  cat(Mod4Step1_txt$exercise)

	cat(Mod4Step1_txt$para1)
	
	  cat(placeholder_image)

	  
	cat(Mod4Step1_txt$results)
	
	# Equation
	cat(Mod4Step1_txt$results_eq1)
	
	cat(Mod4Step1_txt$para2)
```

```{r ex6-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)

get_data <- function(n,r,Vi,Vr, beta){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
  parameters=list(
    Individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    ),
     observation = list(
      names = "X1",
      beta = beta
    )
  ),
    response_names = "Phenotype"
)
  data <- get_population_data(squid_data)
  return(data)

}
```

```{r ex6, exercise=TRUE}
data <- get_data(n = 50, r = 2,  
                 Vi = 0.5, Vr = 0.5, 
                 beta = -0.4)
LMM <- lmer(Phenotype ~ 1 + X1 + (1|Individual), data = data)
summary(LMM)
```

```{r mod4_step1_con, results="asis"}

	cat(Mod4Step1_txt$para3)

	cat(Mod4Step1_txt$para4)

	# Equation
	cat(Mod4Step1_txt$para4_eq1)
```  


```{r ex7-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)

get_data <- function(n,r,Vi,Vr, beta){
  if(length(beta)!=2)stop("beta should be of length 2")
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
  parameters=list(
    Individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    ),
     observation = list(
      names = c("X1","X2"),
      beta = beta
    )
  ),
    response_names = "Phenotype"
)
  data <- get_population_data(squid_data)

  return(data)

}
```

```{r ex7, exercise=TRUE}
data <- get_data(n = 50, r = 2,  
                 Vi = 0.5, Vr = 0.5, 
                 beta = c(-0.4,0.2))
LMM <- lmer(Phenotype ~ 1 + X1 + X2 + (1|Individual), data = data)
summary(LMM)
```

```{r mod4_step1_con2, results="asis"}


	cat(Mod4Step1_txt$para5)


	cat(Mod4Step1_txt$para6)

	cat(Mod4Step1_txt$para7)

	cat(placeholder_image)
	
	cat(Mod4Step1_txt$para8)

  cat(Mod4Step1_txt$conclusion)

  p(strong("References"))
  p(HTML("Allegue, H., Araya-Ajoy, Y.G., Dingemanse, N.J., Dochtermann N.A., Garamszegi, L.Z., Nakagawa, S., Reale, D., Schielzeth, H.
  			 and Westneat, D.F. (2016). SQuID - Statistical Quantification of Individual Differences: an educational and
  			 statistical tool for understanding multi-level phenotypic data in linear mixed models.
  			 <i>Methods in Ecology and Evolution</i>, 8, 257-267. 
         <a href='https://doi.org/10.1111/2041-210X.12659' target='_blank'>doi: 10.1111/2041-210X.12659</a>"))
  
```

```{r mod4_step2_title, results="asis"}
cat("###",Mod4Step2_txt$title)
```

```{r mod4_step2, results="asis"}
# Sub-goal
  cat(Mod4Step2_txt$goal)

  # Introduction
  cat(Mod4Step2_txt$intro)
  
  
  # Exercise
  cat(Mod4Step2_txt$exercise)

  cat(placeholder_image)

  cat(Mod4Step2_txt$results)
  
	# Equation 1
  cat(Mod4Step2_txt$results_eq1)
  
  displayRCode("# install.packages(&quot;lme4&quot;)<br>
                 LMM <- lme4::lmer(Phenotype ~ 1 + X1 + X2 + (1|Individual), data = sampled_data)")
```

```{r mod4_step2_con, results="asis"}

  cat(Mod4Step2_txt$para1)

  # Equation 2
  cat(Mod4Step2_txt$para1_eq1)
```

```{r ex8-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)

get_data <- function(n,r,Vi,Vr, beta,beta2){
  if(length(beta)!=2)stop("beta should be of length 2")
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
  parameters=list(
    Individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    ),
     observation = list(
      names = c("X1","X2"),
      beta = beta
    ),
      interactions=list(
      names=c("X1:X2"),
      beta = beta[3]
    )
  ),
    response_names = "Phenotype"
)
  data <- get_population_data(squid_data)

  return(data)

}
```

```{r ex8, exercise=TRUE}
data <- get_data(n = 50, r = 2,  
                 Vi = 0.5, Vr = 0.5, 
                 beta = c(-0.4,0.2,1))
LMM <- lmer(Phenotype ~ 1 + X1 * X2 + (1|Individual), data = data)
summary(LMM)
```

```{r mod4_step2_con2, results="asis"}
  cat(Mod4Step2_txt$para2)

  cat(Mod4Step2_txt$para3)

  cat(Mod4Step2_txt$conclusion)
```


## Module 5: MDPP and random regression

```{r mod5_step1_title, results="asis"}
cat("###",Mod5Step1_txt$title)
```
```{r mod5_step1, results="asis"}
  # Sub-goal
  cat(Mod5Step1_txt$goal)

  # Introduction
  cat(Mod5Step1_txt$intro)

  # Exercise
  cat(Mod5Step1_txt$exercise)

  # Equation
  cat(Mod5Step1_txt$exercise_eq1)
  
  cat(Mod5Step1_txt$para1)
  
  cat(Mod5Step1_txt$para2)
  
  cat(Mod5Step1_txt$para3)

  cat(Mod5Step1_txt$para4)
  
  cat(placeholder_image)
```

```{r ex12-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)

get_data <- function(n,r,Vi,Vr,Vs, Cis, beta){
  if(length(beta)!=3)stop("Beta should be of length 3.")
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
   parameters = list(
    Individual = list(
      names = c("ind_int","ind_slope"), 
      beta = c(1,0),
      vcov = matrix(c(Vi,Cis,Cis,Vs),ncol=2,nrow=2)
    ),
    observation= list(
      names = c("X1","X2"),
      beta = beta[1:2]
    ), 
    residual = list(
      vcov = Vr
    ),
    interactions = list(
      names = c("ind_slope:X1","X1:X2"),
      beta = c(1,beta[3])
      
  )
  ),
  response_names = "Phenotype"
)
  data <- get_population_data(squid_data)
  return(data)

}
```

```{r ex12, exercise=TRUE}
data <- get_data(n = 300, r = 100,  
                 Vi = 1, Vr = 0.5, Vs = 1e-15, 
                 Cis = 0, 
                 beta = c(-0.4,0.5,2))
LMM <- lmer(Phenotype ~ 1 + X1*X2 + (1 |Individual), data = data)
data2 <- get_data(n = 300, r = 100, 
                  Vi = 1, Vr = 0.5, Vs = 1, 
                  Cis = 0.3, 
                  beta = c(-0.4,0.5,2))
LMM2 <- lmer(Phenotype ~ 1 + X1*X2 + (1 + X1|Individual), data = data2)
```

```{r mod5_step1_con, results="asis"}
  cat(Mod5Step1_txt$para5)
  cat(Mod5Step1_txt$para6)
    
  cat(Mod5Step1_txt$para7)

  cat(Mod5Step1_txt$para8)

  # Exercise
  cat(Mod5Step1_txt$exercise)
  
  cat(Mod5Step1_txt$exercise_eq1)
  
  cat(Mod5Step1_txt$para9)
  
  cat(Mod5Step1_txt$para9_eq1)

  cat(Mod5Step1_txt$para10)
  
  cat(placeholder_image)
  
  cat(Mod5Step1_txt$para11)

```
```{r ex13-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)

get_data <- function(n,r,Vi,Vr,Vs, Cis,Css, beta){
  if(length(beta)!=3)stop("Beta should be of length 3.")
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
   parameters = list(
    Individual = list(
      names = c("ind_int","ind_slope","ind_slope2"), 
      beta = c(1,0,0),
      vcov = matrix(c(Vi,Cis,Cis,Cis,Vs,Css,Cis,Css,Vs),ncol=3,nrow=3)
    ),
    observation= list(
      names = c("X1","X2"),
      beta = beta[1:2]
    ), 
    residual = list(
      vcov = Vr
    ),
    interactions = list(
      names = c("ind_slope:X1","ind_slope2:X2","X1:X2"),
      beta = c(1,1,beta[3])
      
  )
  ),
  response_names = "Phenotype"
)
  data <- get_population_data(squid_data)
  return(data)

}
```

```{r ex13, exercise=TRUE}
data <- get_data(n = 300, r = 100,  
                 Vi = 1, Vr = 0.5, Vs = 1, 
                 Cis = 0.3, Css = 0.5,
                 beta = c(-0.4,0.5,2))
LMM <- lmer(Phenotype ~ 1 + X1*X2 + (1 + X1 + X2|Individual), data = data)
summary(LMM)
```

```{r mod5_step1_con2, results="asis"}
  cat(Mod5Step1_txt$para12)
```
```{r mod5_step2_title, results="asis"}
cat("###",Mod5Step2_txt$title)
```
```{r mod5_step2, results="asis"}
  cat(Mod5Step2_txt$intro)


  cat(Mod5Step2_txt$para1)
  cat(Mod5Step2_txt$para1_eq1)
  
  cat(Mod5Step2_txt$para2)
  cat(Mod5Step2_txt$para2_eq1)
  
  cat(Mod5Step2_txt$para3)
  
  cat(Mod5Step2_txt$para4)
  cat(placeholder_image)

  cat(Mod5Step2_txt$para5)
  cat(Mod5Step2_txt$para5_eq1)
```

```{r mod5_step2_con, results="asis"}
  cat(Mod5Step2_txt$para6)
  cat(Mod5Step2_txt$para6_eq1)

```

```{r ex14-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)

get_data <- function(n,r,Vi,Vr,Vs, Vssi, Cis, Cisi, Css, Cssi, beta){
  if(length(beta)!=3)stop("Beta should be of length 3.")
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
   parameters = list(
    Individual = list(
      names = c("ind_int","ind_slope","ind_slope2","ind_slope3"), 
      beta = c(1,0,0,0),
      vcov = matrix(c(Vi,Cis,Cis,Cisi, Cis, Vs,Css,Cssi,Cis,Css, Vs,Cssi,Cisi,Cssi,Cssi,Vssi),ncol=4,nrow=4)
    ),
    observation= list(
      names = c("X1","X2"),
      beta = beta[1:2]
    ), 
    residual = list(
      vcov = Vr
    ),
    interactions = list(
      names = c("ind_slope:X1","ind_slope2:X2","ind_slope3:X1:X2","X1:X2"),
      beta = c(1,1,1,beta[3])
  )
  ),
  response_names = "Phenotype"
)
  data <- get_population_data(squid_data)
  return(data)

}
```

```{r ex14, exercise=TRUE}
data <- get_data(n = 100, r = 30, 
                 Vi = 1, Vr = 0.5, Vs = 1, Vssi = 2,
                 Cis = 0.3, Cisi = 0.2, Css = 0.5, Cssi = -0.4 , 
                 beta = c(-0.4,0.5,2))
LMM <- lmer(Phenotype ~ 1 + X1*X2 + (1+X1*X2|Individual), data = data)
summary(LMM)

```

```{r mod5_step2_con2, results="asis"}
##Q from text:
#"Run this simulation several times with different values for the interaction term and the covariance terms. Where does the interaction term create the most phenotypic variance and how do covariances affect this?"

  cat(Mod5Step2_txt$para7)

  # Conclusion
  cat(Mod5Step2_txt$conclusion)
```


## Module 6: Multiple traits

```{r mod6_step1_title, results="asis"}
cat("###", Mod6Step1_txt$title)
```

```{r mod6_step1, results="asis"}
# Sub-goal
cat(Mod6Step1_txt$goal)

# Introduction
cat(Mod6Step1_txt$intro)

cat(Mod6Step1_txt$para1)

cat(Mod6Step1_txt$exercise_eq1)

cat(Mod6Step1_txt$para2)

cat(Mod6Step1_txt$para2_eq1)

# Exercise
cat(Mod6Step1_txt$exercise)

cat(Mod6Step1_txt$para3)

cat(placeholder_image) #app 17

cat(Mod6Step1_txt$para4)

cat(Mod6Step1_txt$para4_eq1)

cat(Mod6Step1_txt$para5)

cat(Mod6Step1_txt$conclusion)
```

```{r mod6_step2_title, results="asis"}
cat("###",Mod6Step2_txt$title)
```

```{r mod6_step2, results="asis"}
# Sub-goal
cat(Mod6Step2_txt$goal)

# Introduction
cat(Mod6Step2_txt$intro)

### Model equations
cat(Mod6Step2_txt$intro_eq1)

cat(Mod6Step2_txt$para1)

####### eq 1
cat(Mod6Step2_txt$para1_eq1)

cat(Mod6Step2_txt$para2)

####### eq 2 
cat(Mod6Step2_txt$para2_eq1)

cat(Mod6Step2_txt$para3)

cat(Mod6Step2_txt$para4)

cat(Mod6Step2_txt$para4_eq1)

cat(Mod6Step2_txt$exercise)

cat(placeholder_image) #18

cat(Mod6Step2_txt$para5)
cat(Mod6Step2_txt$para5_eq1)

cat(Mod6Step2_txt$para6)
cat(Mod6Step2_txt$para6_eq1)

cat(Mod6Step2_txt$para7)

####### eq 1
cat(Mod6Step2_txt$para1_eq1)

cat(Mod6Step2_txt$para8)

cat(Mod6Step2_txt$para8_eq1)

cat(Mod6Step2_txt$para9)

cat(Mod6Step2_txt$conclusion)

p(strong("References"))
p(HTML("Dingemanse, N.J. & Dochtermann, N.A. (2013) Quantifying individual variation in behaviour: 
         mixed-effect modelling approaches. <i>Journal of Animal Ecology</i>, 82, 39-54.
         <a href='https://doi.org/10.1111/1365-2656.12013' target='_blank'>doi: 10.1111/1365-2656.12013</a>"))
p(HTML('Dingemanse, N.J., Dochtermann, N.A. & Nakagawa, S. (2012) Defining behavioural syndromes and the role of 
         "syndrome deviation" to study its evolution. <i>Behavioral Ecology and Sociobiology</i>, 66, 1543-1548.
         <a href="https://doi.org/10.1007/s00265-012-1416-2" target="_blank">doi: 10.1007/s00265-012-1416-2</a>'))
p(HTML("Nicolaus, M., Brommer, J.E., Ubels, R., Tinbergen, J.M. & Dingemanse, N.J. (2013) 
          Exploring patterns of variation in clutch size-density reaction norms in a wild passerine bird. 
          <i>Journal of Evolutionary Biology</i>, 26, 2031-2043.
          <a href='https://doi.org/10.1111/jeb.12210' target='_blank'>doi: 10.1111/jeb.12210</a>"))

```

```{r mod6_step3_title, results="asis"}
cat("###",Mod6Step3_txt$title)
```

```{r Mod6Step3, results="asis"}
# Sub-goal
cat(Mod6Step3_txt$goal)	

cat(Mod6Step3_txt$intro)

# Exercise
cat(Mod6Step3_txt$exercise)	

cat(placeholder_image) # app 19

cat(Mod6Step3_txt$results)
cat(Mod6Step3_txt$results_eq1)

cat(Mod6Step3_txt$para1)
cat(Mod6Step3_txt$para1_eq1)


cat(Mod6Step3_txt$para2)

cat(Mod6Step3_txt$para2_eq1)

cat(Mod6Step3_txt$para3)

cat(Mod6Step3_txt$para4)

cat(Mod6Step3_txt$conclusion)

p(strong("References"))
p(HTML("van Noordwijk, A.J. & de Jong, G. (1986) Acquisition and allocation of resources - 
	       Their influence on variation in life-history tactics. <i>American Naturalist</i>, 128, 137-142.
	       <a href='https://doi.org/10.1086/284547' target='_blank'>doi: 10.1086/284547</a>"))
```

```{r mod6_step4_title,results="asis"}
cat("###",Mod6Step4_txt$title)
```

```{r mod6_step4,results="asis"}
# Sub-goal
cat(Mod6Step4_txt$goal)


cat(Mod6Step4_txt$intro)

cat(Mod6Step4_txt$intro_eq1)

cat(Mod6Step4_txt$para1)

cat(Mod6Step4_txt$para1_eq1)

cat(Mod6Step4_txt$para2)

cat(Mod6Step4_txt$para2_eq1)

cat(Mod6Step4_txt$para3)

cat(Mod6Step4_txt$para3_eq1)

cat(Mod6Step4_txt$para4)


cat(Mod6Step4_txt$para4_eq1)

cat(Mod6Step4_txt$para5)

cat(Mod6Step4_txt$para5_eq1)

cat(Mod6Step4_txt$para6)

cat(Mod6Step4_txt$para6_eq1)

cat(Mod6Step4_txt$para7)

cat(Mod6Step4_txt$para7_eq1)

cat(Mod6Step4_txt$para8)

cat(Mod6Step4_txt$para8_eq1)

cat(Mod6Step4_txt$conclusion)
```

```{r mod6_step5_title, results = "asis"}
cat("###",Mod6Step5_txt$title)
```

```{r mod6_step5, results = "asis"}
# Sub-goal
cat(Mod6Step5_txt$goal)

# Introduction
cat(Mod6Step5_txt$intro)

cat(Mod6Step5_txt$intro_eq1)

cat(Mod6Step5_txt$para1)

cat(Mod6Step5_txt$para1_eq1)

cat(Mod6Step5_txt$para2)

# Exercise
cat(Mod6Step5_txt$exercise)

cat(placeholder_image) # app 21

cat(Mod6Step5_txt$para3)

cat(Mod6Step5_txt$para3_eq1)

cat(Mod6Step5_txt$para4)

cat(Mod6Step5_txt$para4_eq1)
```

```{r ex5-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(brms)
library(squidSim)

get_data <- function(n,r,Vi,Vr){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
    data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
    n_response = 2,
    parameters=list(
      observation = list(
        names = "food_availability",
        beta = matrix(c(2,1),ncol=2)
      ),
      Individual = list(
        vcov = matrix(c(1,Vi,Vi,1),nrow=2,ncol=2)
      ),
      residual = list(
        vcov = matrix(c(1,Vr,Vr,1),nrow = 2,ncol = 2)
      )
    ),
    response_names = c("Phenotype_1","Phenotype_2")
  )
  data <- get_population_data(squid_data)
  return(data)
  
}
```

```{r ex5, exercise=TRUE, exercise.timelimit	= 300}
data <- get_data(n = 50, r = 2,  
                 Vi = 0.5, Vr = 0.5)
bLMM <- brm(mvbind(Phenotype_1, Phenotype_2) ~ (1|Individual), data = data, silent = 0)
summary(bLMM)
```

```{r mod6_step5_con,results="asis"}
cat(Mod6Step5_txt$para5)

cat(Mod6Step5_txt$para5_eq1)
```

```{r ex5a-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(brms)
library(squidSim)

get_data <- function(n,r,Vi,Vr){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
    data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
    n_response = 2,
    parameters=list(
      observation = list(
        names = "food_availability",
        beta = matrix(c(2,1),ncol=2)
      ),
      Individual = list(
        vcov = matrix(c(1,Vi,Vi,1),nrow=2,ncol=2)
      ),
      residual = list(
        vcov = matrix(c(1,Vr,Vr,1),nrow = 2,ncol = 2)
      )
    ),
    response_names = c("Phenotype_1","Phenotype_2")
  )
  data <- get_population_data(squid_data)
  return(data)
  
}
```

```{r ex5a, exercise=TRUE, exercise.timelimit	= 300}
data <- get_data(n = 50, r = 2,  
                 Vi = 0.5, Vr = 0.5)
bLMM <- brm(mvbind(Phenotype_1, Phenotype_2) ~ food_availability + (1|Individual), data = data, silent = 0)
summary(bLMM)
```

```{r mod6_step5_con2, results="asis"}
cat(Mod6Step5_txt$para6)

cat(Mod6Step5_txt$conclusion)
```


## (optional) Save progress report

```{r context="setup"}
submission_ui
```

```{r context="server"}
submission_server()
```

## Extra 1: Non-Gaussian traits

```{r extra1_step1_title, results="asis"}
  cat("###", extra$Extra1Step1_txt$title)
```

```{r extra1_step1, results="asis"}
  #### goal ####
  cat(extra$Extra1Step1_txt$goal)
  
  #### Introduction ####
  cat(extra$Extra1Step1_txt$intro)

  cat(extra$Extra1Step1_txt$para1)
  
  
  cat(extra$Extra1Step1_txt$para1_image)
  cat(extra$Extra1Step1_txt$para1_image_caption)

  cat(extra$Extra1Step1_txt$para2)
  
  cat(placeholder_image) #app 5

  cat(extra$Extra1Step1_txt$para3)

  cat(placeholder_image) #app 6

  cat(extra$Extra1Step1_txt$para6)

  cat(extra$Extra1Step1_txt$para4)
  
  cat(placeholder_image) #app 7

  cat(extra$Extra1Step1_txt$para5)
  
  cat(extra$Extra1Step1_txt$exercise)
  
  cat(placeholder_image) #app 8

  
  cat(extra$Extra1Step1_txt$para7)

  h4(extra$Extra1Step1_txt$para8_title)  
  
  HTML(extra$Extra1Step1_txt$para8)
  
 h4(extra$Extra1Step1_txt$para9_title)
  
  HTML(extra$Extra1Step1_txt$para9)
  
  HTML(placeholder_image) #app 9
  
 cat(extra$Extra1Step1_txt$para10)


```

```{r extra1_step2_title, results="asis"}
cat("###", extra$Extra1Step2_txt$title)
```

```{r extra1_step2, results="asis"}
  #### goal ####
  cat(extra$Extra1Step2_txt$goal)
  
  #### Introduction ####
  cat(extra$Extra1Step2_txt$intro)
  
  cat(extra$Extra1Step2_txt$para1)
  
  cat(extra$Extra1Step2_txt$para1_eq1)
  cat(extra$Extra1Step2_txt$para1_eq2)
  cat(extra$Extra1Step2_txt$para1_eq3)
  
  cat(extra$Extra1Step2_txt$para2)
  
  cat(extra$Extra1Step2_txt$para2_eq1)
  cat(extra$Extra1Step2_txt$para2_eq2)
  cat(extra$Extra1Step2_txt$para2_eq3)
 
  cat(extra$Extra1Step2_txt$para3)
  
  cat(extra$Extra1Step2_txt$para3_eq1)
  cat(extra$Extra1Step2_txt$para3_eq2)
  cat(extra$Extra1Step2_txt$para3_eq3)
  
  cat(extra$Extra1Step2_txt$para4)
  
  cat(extra$Extra1Step2_txt$para4_eq1)
  
  cat(extra$Extra1Step2_txt$exercise)

  cat(placeholder_image) #app 10

```

```{r extra1_step3_title, results="asis"}
cat("###", extra$Extra1Step3_txt$title)
```

```{r extra1_step3, results="asis"}
#### goal ####
  cat(extra$Extra1Step3_txt$goal)

  #### Introduction 1 ####
  cat(extra$Extra1Step3_txt$para1)
  
  
  cat(extra$Extra1Step3_txt$para1_eq1)
  cat(extra$Extra1Step3_txt$para1_eq2)
  cat(extra$Extra1Step3_txt$para1_eq3)
  
  cat(extra$Extra1Step3_txt$exercise)
  
```

```{r ex2, exercise=TRUE, warning=F, message=F}
# number of values generated
n <- 10000
# Use the Gaussian distribution to generate n values
# with a mean of 0 and a standard-deviation of 1.
y_prime <- rnorm(n, 0, 1)
# Convert these values to probabilities
# using the inverse-logit function.
p <- plogis(y_prime)
# Use the Bernoulli distribution to generate n values
# with the probability vector p.
y <- rbinom(n, size = 1, prob = p)
# Note that we used the binomial function with one trial,
# which is equivalent to the Bernoulli distribution.
```

```{r extra1_step3_con, results="asis"}
  cat(extra$Extra1Step3_txt$para2)

  #### Introduction 2 ####
  cat(extra$Extra1Step3_txt$intro2)
  
  cat(extra$Extra1Step3_txt$intro2_eq1)
  cat(extra$Extra1Step3_txt$intro2_eq2)
  cat(extra$Extra1Step3_txt$intro2_eq3)
  cat(extra$Extra1Step3_txt$intro2_eq4)

  cat(extra$Extra1Step3_txt$para3)
  
  cat(extra$Extra1Step3_txt$para4)
  
  cat(extra$Extra1Step3_txt$para4_eq1)
  cat(extra$Extra1Step3_txt$para4_eq2)
  cat(extra$Extra1Step3_txt$para4_eq3)
  cat(extra$Extra1Step3_txt$para4_eq4)

  cat(extra$Extra1Step3_txt$exercise2)
  
  cat(placeholder_image) #app11

```

```{r ex3-setup, exercise=TRUE, warning=FALSE, message=FALSE, echo=TRUE, exercise.cap = "Set-up for exercise code chunk."}
library(lme4)
library(squidSim)
get_data <- function(n,r,Vi,Vr){
  if(n>1000)stop("Please don't make our server hamsters work that hard..")
  squid_data <- simulate_population(
  data_structure = make_structure(structure = paste0("Individual(",n,")"), repeat_obs=r),
  parameters = list(
    Individual = list(
      vcov = Vi
    ),
    residual = list(
      vcov = Vr
    )
  ),
  family = "poisson", 
  link = "log",
  response_names = "Phenotype"
)
  data <- get_population_data(squid_data)
  return(data)
}
```

```{r ex3, exercise=TRUE, exercise=TRUE, warning=FALSE, message=FALSE}
# n is the number of individuals
# r is the number of repetitions for each individual
# Vi is the variance for individuals
# Vr is residual variance 
data <- get_data(n = 50, r = 2, Vi = 0.5, Vr = 0.5)
GLMM <- glmer(Phenotype ~ 0 + (1|Individual), family = poisson(link=log), data = data)
summary(GLMM)
```

```{r extra1_step3_con2, results="asis"}
  cat(extra$Extra1Step3_txt$conclusion)
```
